Paper figures

### 2020-03-21 voltagebudget/analysis/paper_figures_lossy.Rmd
- Added Fig 8 and 9 - Tweak labels/colors in others

# Figure 8 - error50

HERE - need to add osc shit examples to the top of this figure. Next up is E50 intro figure.

```{r, message=FALSE}
# --------------------------------------------------------------------
vb_results <- NULL

@@

# Ratio ests
vb_mean_results_ratios <- NULL
freqs <- unique(vb_mean_results$freq)
for (f in freqs) {
  tmp <- filter(vb_mean_results, f == freq, V_osc/V_comp < 5)
  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
  row <- c(pnts, f)
  vb_mean_results_ratios <- rbind(vb_mean_results_ratios, row)
}
vb_mean_results_ratios <- as.data.frame(vb_mean_results_ratios, stringsAsFactors=FALSE)
colnames(vb_mean_results_ratios) <- c("error_50", "ratio", "freq")
```
```{r, message=FALSE, fig.width=4, fig.height=1.8}

@@

vb_norm_results %>% 
  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
  ggplot(aes(y=variances_pop*ms, x=errors_pop*ms, group=N, color=As)) +
  geom_point(alpha=0.8, size=1) +
  labs(x="Error (ms)", y="Compression (ms)") +
  lims(y=c(7,9)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  ggtitle("The compression/error trade-off") +
  theme_classic() -> p3

((p1 / p2) | p3) +
  plot_layout(widths = c(1, 2)) + 
  plot_annotation(tag_levels = 'a', tag_suffix = ".")
```

>>>>

# Figure 8 - osc intro
```{r, fig.width=2, fig.height=1, message=FALSE}
# Load example spikes
ref_times <- read_csv("../../data/stim1.csv")
ref_times %>% 
   mutate(ts = ts - min(ts)) -> ref_times

# Make waves a function
time <- seq(0,0.4*2,length.out=1000)
freq <- 8
A <- 1
wave <- A/2 + A/2*sin(freq * time)

# As a test, plot an example of the wave
# plot(time, wave, xlab = "Time", ylab="Amplitude (namps)")

# Build a wave datafrome
amps <- c(
  min(vb_results$As[vb_results$As > 0]), 
  median(vb_results$As[vb_results$As > 0]), 
  max(vb_results$As[vb_results$As > 0]))

wave_results <- NULL
for (a in amps){
  df <- data.frame(time=time, 
                   wave=a*wave, 
                   As=rep(a, length(time)))
  wave_results <- bind_rows(wave_results, df)
}

# TODO - run simulations with As from above

```
```{r, fig.width=3, fig.height=2, message=FALSE}
# Make the figure
p1 <- ref_times %>% 
  ggplot(aes(x=ts*1e3, y=ns)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  ggtitle("Original\nmessage")

p2 <- wave_results %>% 
  ggplot(aes(x=time, y=wave, color=As, group=As)) +
  geom_line() +
  labs(x="Time (ms)", y="Amplitude") +
  lims(x=c(0, 0.8)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  theme_classic() +
  ggtitle("Compression\n'algorithm'")

# HERE - need to run sims to make the osc_times df
p3 <- osc_times %>% 
  ggplot(aes(x=ts*1e3, y=ns, color=As)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  facet_grid(.~As) +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  ggtitle("Compression\nby oscillation")

# Build figure 
(p1 | p2) / p3 +
  plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = 'a', tag_suffix = ".")
ggsave("figures/lossy_fig8.png", dpi=600)
```

# Figure 9 - trade-off (with osc)
```{r, message=FALSE}
# --------------------------------------------------------------------
vb_results <- NULL

@@

# Ratio ests
vb_mean_results_ratios <- NULL
freqs <- unique(vb_mean_results$freq)
for (f in freqs) {
  tmp <- filter(vb_mean_results, f == freq, V_osc/V_comp < 5)
  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
  row <- c(pnts, f)
  vb_mean_results_ratios <- rbind(vb_mean_results_ratios, row)
}
vb_mean_results_ratios <- as.data.frame(vb_mean_results_ratios, stringsAsFactors=FALSE)
colnames(vb_mean_results_ratios) <- c("error_50", "ratio", "freq")
```
```{r, message=FALSE, fig.width=3.8, fig.height=1.8}

@@

vb_norm_results %>% 
  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
  ggplot(aes(y=variances_pop*ms, x=errors_pop*ms, group=N, color=As)) +
  geom_point(alpha=0.8, size=1) +
  labs(x="Error (ms)", y="Compression (ms)") +
  lims(y=c(7,9)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  ggtitle("Compression/error trade-off\nfor oscillation") +
  theme_classic() -> p3

((p1 / p2) | p3) +
  plot_layout(widths = c(1, 2)) + 
  plot_annotation(tag_levels = 'a', tag_suffix = ".")
ggsave("figures/lossy_fig9.png", dpi=600)
```
